Combat Sandbox

### 2023-10-12 ukb_combat.Rmd
write out combatted dfs

simple combat with no covariate preservation
```{r}
cf <- comfam(pheno.df, batch)
cf$dat.combat
```

simple combat with linear model for covariates
```{r}
cf.lm <- comfam(pheno.df, batch, covar.mat, lm, formula = y ~ age_days + sexMale)
cf.lm$dat.combat
```
add site
```{r}
#add back site
#cf.lm$dat.combat[, "sim.site"] <- batch
```

@@

```{r}
cf.lm_refA <- comfam(pheno.df, batch, covar.mat, lm, formula = y ~ age_days + sexMale, ref.batch = "Site_A")
cf.lm_refA$dat.combat
# cf.lm_refA$dat.combat[, "sim.site"] <- batch
```

combat gam with age as smooth
```{r}
cf.gam <- comfam(pheno.df, batch, covar.mat, gam, formula = y ~ s(age_days) + sexMale)
# cf.gam$dat.combat[, "sim.site"] <- batch
```

```{r}
cf.gam_refA <- comfam(pheno.df, batch, covar.mat, gam, formula = y ~ s(age_days) + sexMale, ref.batch = "Site_A")
# cf.gam_refA$dat.combat[, "sim.site"] <- batch
```

@@

```{r}
cf.gamlss <- comfam(pheno.df, batch, covar.mat, gamlss, y ~ age_days + sexMale,
              sigma.formula = ~ age_days + sexMale, 
              control = gamlss.control(trace = FALSE))
# cf.gamlss$dat.combat[, "sim.site"] <- batch
```

```{r}
cf.gamlss_refA <- comfam(pheno.df, batch, covar.mat, gamlss, y ~ age_days + sexMale,
              sigma.formula = ~ age_days + sexMale, 
              control = gamlss.control(trace = FALSE),
              ref.batch = "Site_A")
# cf.gamlss_refA$dat.combat[, "sim.site"] <- batch
```

@@

>>>>

simple combat with no covariate preservation
```{r}
cf <- comfam(pheno.df, batch)
# cf$dat.combat
```

simple combat with linear model for covariates
```{r}
cf.lm <- comfam(pheno.df, batch, covar.mat, lm, formula = y ~ age_days + sexMale)
# cf.lm$dat.combat
```

@@

```{r}
cf.lm_refA <- comfam(pheno.df, batch, covar.mat, lm, formula = y ~ age_days + sexMale, ref.batch = "Site_A")
# cf.lm_refA$dat.combat
```

combat gam with age as smooth
```{r}
cf.gam <- comfam(pheno.df, batch, covar.mat, gam, formula = y ~ s(age_days) + sexMale)
```

```{r}
cf.gam_refA <- comfam(pheno.df, batch, covar.mat, gam, formula = y ~ s(age_days) + sexMale, ref.batch = "Site_A")
```

@@

```{r}
cf.gamlss <- comfam(pheno.df, batch, covar.mat, gamlss, y ~ age_days + sexMale,
              sigma.formula = ~ age_days + sexMale, 
              control = gamlss.control(trace = FALSE))
```

```{r}
cf.gamlss_refA <- comfam(pheno.df, batch, covar.mat, gamlss, y ~ age_days + sexMale,
              sigma.formula = ~ age_days + sexMale, 
              control = gamlss.control(trace = FALSE),
              ref.batch = "Site_A")
```

@@

write out
```{r}
for (i in names(combat.df.list)){
  df <- combat.df.list[[i]] %>%
  write_csv(df, file=paste0("data/ukb_to_model/ukb_", as.character(i), "_data.csv"))
}
```
